Wikipedia WALS Feature Analysis

### 2019-07-17 surprisal/WALS_features.Rmd
changes

all_distances %>% 
  ggplot(aes(x = feature)) +
    geom_smooth(aes(y = unigram_cosine, color = "#0033CC"), 
                method = 'lm', se = F) + 
    geom_smooth(aes(y = bigram_cosine, color = "#6699FF"), 
                method = 'lm', se = F) +
    geom_smooth(aes(y = trigram_cosine, color = "#33CCFF"), 
                method = 'lm', se = F) +
    ylab("Cosine Space Distance") + 
    xlab("Feature Space Distance") + 
    scale_color_manual(scale_name = "gram", 
                       values = c("#0033CC", "#6699FF", "#33CCFF"), 
                       labels = c("Unigrams", "Bigrams", "Trigrams")) + 
    ggtitle("Cosine space distance regressed on feature spaced distance")
```

>>>>

all_distances %>% 
  ggplot(aes(x = feature)) +
    geom_smooth(aes(y = unigram_cosine, color = "#0033CC"), 
                method = 'lm', se = F) + 
    geom_smooth(aes(y = bigram_cosine, color = "#6699FF"), 
                method = 'lm', se = F) +
    geom_smooth(aes(y = trigram_cosine, color = "#33CCFF"), 
                method = 'lm', se = F) +
    geom_point(aes(y = unigram_cosine, color = "#0033CC")) + 
    geom_point(aes(y = bigram_cosine, color = "#6699FF")) + 
    geom_point(aes(y = trigram_cosine, color = "#33CCFF")) + 
    ylab("Cosine Space Distance") + 
    xlab("Feature Space Distance") + 
    scale_color_manual(name = "Gram", 
                       values = c("#0033CC", "#6699FF", "#33CCFF"), 
                       labels = c("Unigrams", "Bigrams", "Trigrams")) + 
    ggtitle("Cosine space distance regressed on feature spaced distance")
```
